### 2016-04-17 lineups.Rnw
table shows means from simulation

\begin{table}[h]
\caption{\label{tab:models}Parameters and estimates of models $M_1$ and $M_2$. \hh{Estimates stem from one of the simulations. XXX We probably should change that to the average of the 1000 simulations, and then simulate the lineups from those, like you suggested. }}
\centering
\scalebox{0.8}{
\begin{tabular}{lccrr}
Effect name & Parameter & Corresponding Statistic & $M_1$ Estimate & $M_2$ Estimate\\
\hline
\hline
Rate 1 (wave 1 $\rightarrow$ 2) & $\alpha_1$ & $\sum\limits_{i,j = 1 i\neq j}^n (x_{ij}(t_2) - x_{ij}(t_1))^2 $ & \Sexpr{round(lineup1$null_mod_ests[1], 3)} & \Sexpr{round(lineup1$alt_mod_estimates[1],3)}\\
Rate 2 (wave 2 $\rightarrow$ 3) & $\alpha_2$ & $\sum\limits_{i,j = 1 i\neq j}^n (x_{ij}(t_3) - x_{ij}(t_2))^2 $ & \Sexpr{round(lineup1$null_mod_ests[2], 3)} & \Sexpr{round(lineup1$alt_mod_estimates[2],3)}\\
Outdegree & $\beta_1$ & $s_{i1}(x) = \sum\limits_{j=1}^n x_{ij}$ & \Sexpr{round(lineup1$null_mod_ests[3], 3)} & \Sexpr{round(lineup1$alt_mod_estimates[3],3)}\\
Reciprocity & $\beta_2$ & $s_{i2}(x) = \sum\limits_{j=1}^n x_{ij}x_{ji}$ & \Sexpr{round(lineup1$null_mod_ests[4], 3)} & \Sexpr{round(lineup1$alt_mod_estimates[4],3)}\\
Jumping Transitive Triplets & $\beta_3$ & $s_{i3}(x) = \sum\limits_{\forall j\neq h} x_{ij}x_{ih}x_{hj} \mathbb{I}(v_i = v_h \neq v_j)$ & -- & \Sexpr{round(lineup1$alt_mod_estimates[5],3)}
\end{tabular}}
\end{table}

\begin{figure}
\centering
<<hist-estimates, echo=FALSE, fig.width=8, fig.height=5, out.width='.8\\linewidth'>>=
# nulls <- read.csv("Data/distribution_null_model.csv")
# names(nulls)[-1] <- c("alpha1", "alpha2", "beta1", "beta2")
# nulls$Sim <- 1:nrow(nulls)
# nulls$Model <- "M1"
# 
# alt <- read.csv("Data/distribution_jumpTT_model.csv")
# names(alt)[-1] <- c("alpha1", "alpha2", "beta1", "beta2", "beta3")
# alt$Sim <- 1:nrow(alt)
# alt$Model <- "M2"
# 
# alt2 <- gather(alt, parameter, estimate, 2:6)
# null2 <- gather(nulls, parameter, estimate, 2:5)
# 
# simu <- rbind(alt2[,-1], null2[,-1])
# write.csv(simu, "Data/simulation-1000-M1-M2.csv", row.names=FALSE)

simu <- read.csv("Data/simulation-1000-M1-M2.csv")
qplot(data=simu, estimate, fill=Model, geom="density", alpha=I(0.75)) + facet_wrap(~parameter, scales="free") + theme_bw()
@
\caption{\label{fig:hist-simulations}Histogram of the distribution of model parameters based on 1,000 simulation runs. Model parameter $\beta_3$ for jumping transitive triplets in model $M_2$ is significantly different from zero, but its inclusion also leads to significant changes in the  other model parameters of model $M_1$. }
\end{figure}

>>>>

<<readsimu, echo=FALSE>>=
# nulls <- read.csv("Data/distribution_null_model.csv")
# names(nulls)[-1] <- c("alpha1", "alpha2", "beta1", "beta2")
# nulls$Sim <- 1:nrow(nulls)
# nulls$Model <- "M1"
# 
# alt <- read.csv("Data/distribution_jumpTT_model.csv")
# names(alt)[-1] <- c("alpha1", "alpha2", "beta1", "beta2", "beta3")
# alt$Sim <- 1:nrow(alt)
# alt$Model <- "M2"
# 
# alt2 <- gather(alt, parameter, estimate, 2:6)
# null2 <- gather(nulls, parameter, estimate, 2:5)
# 
# simu <- rbind(alt2[,-1], null2[,-1])
# write.csv(simu, "Data/simulation-1000-M1-M2.csv", row.names=FALSE)

simu <- read.csv("Data/simulation-1000-M1-M2.csv")
means <- simu %>% group_by(Model, parameter) %>% summarize(
  mean = mean(estimate)
)
@

\begin{table}[h]
\caption{\label{tab:models}Parameters and estimates of models $M_1$ and $M_2$. \hh{Estimates stem from one of the simulations. XXX We probably should change that to the average of the 1000 simulations, and then simulate the lineups from those, like you suggested. }}
\centering
\scalebox{0.8}{
\begin{tabular}{lccrr}
Effect name & Parameter & Corresponding Statistic & $M_1$ Estimate & $M_2$ Estimate\\
\hline
\hline
Rate 1 (wave 1 $\rightarrow$ 2) & $\alpha_1$ & $\sum\limits_{i,j = 1 i\neq j}^n (x_{ij}(t_2) - x_{ij}(t_1))^2 $ & 
\Sexpr{round(subset(means, Model=="M1" & parameter=="alpha1")$mean, 2)} &
\Sexpr{round(subset(means, Model=="M2" & parameter=="alpha1")$mean, 2)}
\\
Rate 2 (wave 2 $\rightarrow$ 3) & $\alpha_2$ & $\sum\limits_{i,j = 1 i\neq j}^n (x_{ij}(t_3) - x_{ij}(t_2))^2 $ & 
\Sexpr{round(subset(means, Model=="M1" & parameter=="alpha2")$mean, 2)} &
\Sexpr{round(subset(means, Model=="M2" & parameter=="alpha2")$mean, 2)}
\\
Outdegree & $\beta_1$ & $s_{i1}(x) = \sum\limits_{j=1}^n x_{ij}$ & \Sexpr{round(subset(means, Model=="M1" & parameter=="beta1")$mean, 2)} &
\Sexpr{round(subset(means, Model=="M2" & parameter=="beta1")$mean, 2)}
\\
Reciprocity & $\beta_2$ & $s_{i2}(x) = \sum\limits_{j=1}^n x_{ij}x_{ji}$ & \Sexpr{round(subset(means, Model=="M1" & parameter=="beta2")$mean, 2)} &
\Sexpr{round(subset(means, Model=="M2" & parameter=="beta2")$mean, 2)}
\\
Jumping Transitive Triplets & $\beta_3$ & $s_{i3}(x) = \sum\limits_{\forall j\neq h} x_{ij}x_{ih}x_{hj} \mathbb{I}(v_i = v_h \neq v_j)$ & -- & \Sexpr{round(subset(means, Model=="M2" & parameter=="beta3")$mean, 2)}
\end{tabular}}
\end{table}

\begin{figure}
\centering
<<hist-estimates, dependson='read-simu', echo=FALSE, fig.width=8, fig.height=5, out.width='.8\\linewidth'>>=
qplot(data=simu, estimate, fill=Model, geom="density", alpha=I(0.75)) + facet_wrap(~parameter, scales="free") + theme_bw()
@
\caption{\label{fig:hist-simulations}Histogram of the distribution of model parameters based on 1,000 simulation runs. Model parameter $\beta_3$ for jumping transitive triplets in model $M_2$ is significantly different from zero, but its inclusion also leads to significant changes in the  other model parameters of model $M_1$. }
\end{figure}
